Diagnosing Child Poverty Reduction Interventions

### 2024-09-03 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Fixed problem with nutrition_quality model, and additions to the CPR_Intervention_Diagnostics script

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
#out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 
                                    'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)
# rel.int <- read_singular_local_out(out.path, 
#                                    'ChildPovertyReductionRELATIVE', 
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
rel.int <- read_singular_local_out(out.path,
                                     'ChildPovertyReductionRELATIVE_2',
                                     drop.dead = TRUE,
                                     drop.zero.weight = TRUE)
abs.int <- read_singular_local_out(out.path,
                                   'ChildPovertyReductionABSOLUTE',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
```

@@

rel.inc <- rel.int %>%
  select(pidp, hidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income,w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Relative')

inc <- rbind(base.inc, rel.inc)

ggplot(base.dat, aes(x = hh_income, y = time, group = time, color = 'blue', alpha = 0.3)) +
  geom_density_ridges() +
  geom_density_ridges(data = rel.int, aes(x = hh_income, y = time, group = time, color = 'red')) +
  theme(legend.position = 'none') +
  labs(title = 'Relative Poverty Reduction Intervention - Red')
```

@@

rel.inc <- rel.int %>%
  select(pidp, hidp, time, hh_income, age, nkids, weight) %>%
  mutate(nkids_any = (nkids > 0)) %>%
  filter(nkids_any = TRUE) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Relative')

inc <- rbind(base.inc, rel.inc)

ggplot(inc, aes(x = time, y = hh_income, group = scen, color = scen, fill = scen)) +
  geom_line() +
  geom_point()
```

@@

```{r}
boosted.pidps <- rel.int %>%
  filter(income_boosted == 'True') %>%
  select(pidp)

base.inc <- base.dat %>%
  select(pidp, hidp, time, hh_income, SF_12, weight) %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE),
            SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Baseline')

rel.inc <- rel.int %>%
  select(pidp, hidp, time, hh_income, SF_12, weight) %>%
  filter(pidp %in% boosted.pidps$pidp) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE),
            SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Relative')

inc <- rbind(base.inc, rel.inc)

@@

@@

```{r}
boosted.pidps <- rel.int %>%
  filter(income_boosted == 'True') %>%
  select(pidp, time)

@@

rel.inc <- rel.int %>%
  select(pidp, hidp, time, age, hh_income, SF_12, housing_quality, neighbourhood_safety, ncigs, nutrition_quality, loneliness, nkids, weight) %>%
  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
  mutate_at(vars(housing_quality), ~recode(., !!!recoding_mapping)) %>%
  group_by(time) %>%
  summarise(boosted_pop = n(),
            age = mean(age, na.rm = TRUE),
            hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE),
            SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE),
            housing_quality = weighted.mean(x = housing_quality, w = weight, na.rm = TRUE),
            neighbourhood_safety = weighted.mean(x = neighbourhood_safety, w = weight, na.rm = TRUE),
            ncigs = weighted.mean(x = ncigs, w = weight, na.rm = TRUE),
            nutrition_quality = weighted.mean(x = nutrition_quality, w = weight, na.rm = TRUE),
            loneliness = weighted.mean(x = loneliness, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Relative')

@@

rel.treated <- rel.int %>%
  select(pidp, time, hh_income, SF_12, nutrition_quality, ncigs) %>%
  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
  mutate(scen = 'Intervention')

inc <- rbind(base.inc, rel.inc)
treated <- rbind(base.treated, rel.treated)
```

@@

ggplot(base.treated, aes(x = hh_income, y = time, group = time, alpha = 0.3), color = 'blue') +
  geom_density_ridges() +
  geom_density_ridges(data = rel.treated, aes(x = hh_income, y = time, group = time), color = 'red') +
  theme(legend.position = 'none') +
  labs(title = 'Relative Poverty Reduction Intervention - Red')

@@

@@

rel.housing <- rel.int %>%
  dplyr::select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(scen = 'Intervention')

housing <- rbind(base.housing, rel.housing)
housing$housing_quality <- as.factor(housing$housing_quality)

>>>>

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
#out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 
                                    'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)
int.dat <- read_singular_local_out(out.path,
                               'ChildPovertyReduction',
                               drop.dead = TRUE,
                               drop.zero.weight = TRUE)
# rel.int <- read_singular_local_out(out.path,
#                                      'ChildPovertyReductionRELATIVE_2',
#                                      drop.dead = TRUE,
#                                      drop.zero.weight = TRUE)
# abs.int <- read_singular_local_out(out.path,
#                                    'ChildPovertyReductionABSOLUTE',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
```

@@

int.inc <- int %>%
  select(pidp, hidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income,w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Intervention')

inc <- rbind(base.inc, int.inc)

ggplot(inc, aes(x = time, y = hh_income, group = scen, color = scen, fill = scen)) +
  geom_line() +
  geom_point() +
  labs(title = 'Whole Population')

ggplot(base.dat, aes(x = hh_income, y = time, group = time)) +
  geom_density_ridges(color = 'blue', alpha = 0.3) +
  geom_density_ridges(data = int.dat, aes(color = 'red', alpha = 0.3)) +
  theme(legend.position = 'none') +
  labs(title = 'Relative Poverty Reduction Intervention - Red')
```

@@

int.inc <- int %>%
  select(pidp, hidp, time, hh_income, age, nkids, weight) %>%
  mutate(nkids_any = (nkids > 0)) %>%
  filter(nkids_any = TRUE) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Intervention')

inc <- rbind(base.inc, int.inc)

ggplot(inc, aes(x = time, y = hh_income, group = scen, color = scen, fill = scen)) +
  geom_line() +
  geom_point() +
  labs(title = 'Households with Children')
```

@@

```{r}
boosted.pidps <- int.dat %>%
  filter(income_boosted == 'True') %>%
  select(pidp, time)

#base.inc <- merge(base.dat, boosted.pidps, by = c('pidp', 'time'))
#int.inc <- merge(int.dat, boosted.pidps, by = c('pidp', 'time'))

base.inc <- base.dat %>%
  select(pidp, hidp, time, hh_income, SF_12, weight) %>%
  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE),
            SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Baseline')

int.inc <- int.dat %>%
  select(pidp, hidp, time, hh_income, SF_12, weight) %>%
  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE),
            SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Intervention')

inc <- rbind(base.inc, int.inc)

@@

# Income by Quintile

@@

```{r}
boosted.pidps <- int.dat %>%
  filter(income_boosted == 'True') %>%
  select(pidp, time)

@@

int.inc <- int.dat %>%
  select(pidp, hidp, time, age, hh_income, SF_12, housing_quality, neighbourhood_safety, ncigs, nutrition_quality, loneliness, nkids, weight) %>%
  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
  mutate_at(vars(housing_quality), ~recode(., !!!recoding_mapping)) %>%
  group_by(time) %>%
  summarise(boosted_pop = n(),
            age = mean(age, na.rm = TRUE),
            hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE),
            SF_12 = weighted.mean(x = SF_12, w = weight, na.rm = TRUE),
            housing_quality = weighted.mean(x = housing_quality, w = weight, na.rm = TRUE),
            neighbourhood_safety = weighted.mean(x = neighbourhood_safety, w = weight, na.rm = TRUE),
            ncigs = weighted.mean(x = ncigs, w = weight, na.rm = TRUE),
            nutrition_quality = weighted.mean(x = nutrition_quality, w = weight, na.rm = TRUE),
            loneliness = weighted.mean(x = loneliness, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Intervention')

@@

int.treated <- int.dat %>%
  select(pidp, time, hh_income, SF_12, nutrition_quality, ncigs) %>%
  inner_join(boosted.pidps, by = c("pidp", "time")) %>%
  mutate(scen = 'Intervention')

inc <- rbind(base.inc, int.inc)
treated <- rbind(base.treated, int.treated)
```

@@

ggplot(base.treated, aes(x = hh_income, y = time, group = time, alpha = 0.3), color = 'blue') +
  geom_density_ridges() +
  geom_density_ridges(data = int.treated, aes(x = hh_income, y = time, group = time), color = 'red') +
  theme(legend.position = 'none') +
  labs(title = 'Relative Poverty Reduction Intervention - Red')

@@

```{r}
library(xgboost)
sf12 <- readRDS('/home/luke/Documents/WORK/MINOS/Minos/data/transitions/SF_12/xgb/SF_12_XGB.rds')

xgb.ggplot.shap.summary(sf12)
```

@@

int.housing <- int.dat %>%
  dplyr::select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(scen = 'Intervention')

housing <- rbind(base.housing, int.housing)
housing$housing_quality <- as.factor(housing$housing_quality)
